Determining Causes of Death from Verbal Autopsy with ChatGPT: A Case Study of 6942 Deaths in Sierra Leone from 2019-2022

### 2024-01-17 manuscript/manuscript.tex
Working on methods

\noindent For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first converted into 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 Open Data Kit (ODK) format \cite{nafundiODKCollectData2023}, followed by further conversion into OpenVA format \cite{liOpenVAToolkitVerbal2023} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}, and used as input for InterVA-5 and InSilicoVA. The 6942 physician agreed records were all converted into generated text prompts as ChatGPT-3.5 and ChatGPT-4 inputs. Only 6897 of the 6942 physician agreed records were converted into OpenVA formatted records as InterVA-5 and InSilicoVA inputs as 45 records caused conversion errors and were skipped.

@@

>>>>

\noindent For InterVA-5 and InSilicoVA, the standardized questionnaire data from the HEAL-SL EVA were first converted into 2016 World Health Organization (WHO) VA questionnaire revision 1.5.1 Open Data Kit (ODK) format \cite{nafundiODKCollectData2023}, followed by further conversion into OpenVA format \cite{liOpenVAToolkitVerbal2023} using the \verb|pyCrossVA| Python package \cite{thomasPycrossvaPrepareData}, and used as input for InterVA-5 and InSilicoVA. The 6942 physician agreed records were all converted into generated text prompts as ChatGPT-3.5 and ChatGPT-4 inputs. Only 6897 of the 6942 physician agreed records were converted into OpenVA formatted records as InterVA-5 and InSilicoVA inputs, where 45 records caused conversion errors and were skipped.

@@

The performance of four models, ChatGPT-3.5, ChatGPT-4, InterVA-5, and InSilicoVA, were evaluated with metrics on the population and individual level by comparing their CGHR-10 COD outputs to 6942 physician agreed records. Cause Specific Mortality Fraction (CSMF) accuracy was used to evaluate models on the population level, while Partial Chance Corrected Concordance (PCCC) was used to evaluate models on the individual level. Records that were assigned a COD by physicians, but not by a model were considered to be an incorrect COD assignment by the model.
